RDF Validation of Metadata \\ on Highly-Complex Person-Level Data

### 2015-02-20 paper/paper7/paper7-appendix.tex
RDF Validation of Metadata and Data

\begin{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-01:}}
If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
then the property {\em disco:isValid} has to be stated indicating if the code is valid ('true') or missing ('false').
\end{itemize}

>>>>

\begin{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
		\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
		\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
		\begin{itemize}
		\item severity level: WARNING
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
		\begin{itemize}
		\item severity level: INFO
	\end{itemize}
	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-05}}:
	each (\emph{disco:Variable}) to compare must be present.
	\begin{itemize}
		\item severity level: ERROR
	\end{itemize}
\end{itemize}

@@

\begin{itemize}
	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-01}}:
  If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
then the property {\em disco:isValid} has to be stated indicating if the code is valid ('true') or missing ('false').
	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-02}}:
	If the abstract (\emph{dcterms:abstract}) of a \emph{disco:Study} is missing, a study title (\emph{dcterms:title}) has to be stated.
\end{itemize}

### 2015-02-20 paper/paper7/paper7.tex
RDF Validation of Metadata and Data

\tb{we use data in singular form / we use data set instead of dataset / We use person-level data and not microdata}

@@

-----

- different sets of constraints for different use cases / use case specific constraints

- validation against minimal set of requirements / constraints

-----

severity level:

- use case specific severity levels

- users specify severity level of constraint types according to their individual use case

- for some use case the severity level of a given constraint type may be different as for another use case

-----

@@

- different severity levels for different validation types

@@

\textbf{Studies.}
Each study must have an abstract. 
If an abstract is missing a study title may be sufficient in many cases.

@@

\textbf{Comparison.}

- variable must be present

- code lists must be similar or ideally identical (strong severity level / or weaker severity level if one wants to have only an overview)

(1) variable definitions are available

(2) if code lists are properly structured

(3) if for each code an associated category (a human-readable label) is specified.

@@

%\subsection{Technology-Driven Validation}

@@

>>>>

\tb{terminology: we use data in singular form / we use data set instead of dataset / We use person-level data and not microdata}

@@

Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
This technical report also contains mappings to description logics to logically underpin each requirement and to determine which description logics constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
Bosch et al. recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/XXXXX}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types
\cite{BoschZapilkoWackerowEckert2015}.

We distinguish two validation types:
\emph{Content-Driven Validation} contains the set of constraints ensuring that the data is consistent with the intended semantics of data models,
i.e. the integrity of the data according to data models.
\emph{Technology-Driven Validation} includes the set of constraints which can be generated automatically out of defined data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
We determined the default \emph{severity level}\footnote{Corresponds to \emph{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}} for each constraint indicating how serious the violation of the constraint is.
The continuum of \emph{severity levels} ranges from informational via warning and error to fatal error. 
Although we provide default \emph{severity levels} for each constraint, users should be able to specify \emph{severity levels} of constraints they need to validate within the context of their individual use cases.
Therefore, use case specific \emph{severity levels} can be defined for constraints.

-----
%
%- different sets of constraints for different use cases / use case specific constraints
%
%- validation against minimal set of requirements / constraints
%
%-----

@@

@@

\textbf{Surveys.}
Each survey must have an abstract\footnote{\emph{ DISCO-C-DATA-PROPERTY-FACETS-01}}. 
If the abstract of the survey is missing, a title of the survey has to be stated\footnote{\emph{DISCO-C-CONDITIONAL-PROPERTIES-02}}.

@@

\textbf{Variable Comparisons\footnote{Constraint types: \emph{DISCO-C-COMPARISON-VARIABLES-XX}}.}
One very common research question is to compare variables of multiple surveys or countries.
To compare variables, 
(1) variables and (2) variable definitions must be present,
(3) code lists must be structured properly,
(4) for each code an associated category (human-readable label) must be specified, and
(5) code lists must either be identical or at least similar.
If a researcher wants to get a first overview over comparable variables (use case 1), 
the first three constraints may be sufficient for this purpose.
Thus, the \emph{severity level} of the first three constraints is stronger than the \emph{severity level} of the next constraints.
If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining constraints is also more serious.

@@

@@

\subsection{Technology-Driven Validation}
